\texttt{davos}: a Python package ``smuggler'' for constructing lightweight reproducible notebooks

### 2022-10-28 paper/main.tex
updates to davos config section

\subsubsection{The \texttt{davos} config}\label{subsec:config}
The \texttt{davos} config object provides a simple, high-level interface that allows users to view and set various options that affect \texttt{davos}'s behavior. After importing \texttt{davos}, the config instance (a singleton) for the current session is available as \texttt{davos.config}, and its various fields are accessible as attributes (see Fig.~\textcolor{red}{REF TO ILLUSTRATIVE EXAMPLE FIG} for example usage). The config object exposes a mixture of writable and read-only fields. Writable fields include:
\begin{itemize}
\item \texttt{.active}: Whether or not \texttt{davos} functionality (i.e., support for \texttt{smuggle} statements and onion comments) should be enabled for subsequent code. Defaults to \texttt{True} when \texttt{davos} is first imported. See Section~\ref{subsec:implementation} for additional info.
\item \texttt{.auto\_rerun}: Controls behavior if \texttt{davos} is used to \texttt{smuggle} a new version of a package that was previously imported and cannot be reloaded (i.e., it contains C-extensions that dynamically generate code). If \texttt{True} (default: \texttt{False}), \texttt{davos} will automatically restart the notebook kernel and rerun all code up to (and including) the current \texttt{smuggle} statement. Otherwise, \texttt{davos} will issue a warning, pause execution, and prompt the user with buttons to either restart \& rerun the notebook or continue running with the imported package version. (Note: not configurable in Google Colaboratory).
\item \texttt{.confirm\_install}: If \texttt{True} (default: \texttt{False}), \texttt{davos} will require user confirmation (\texttt{[y]es/[n]o} input) before installing a smuggled package.
\item \texttt{.noninteractive}: Setting to \texttt{True} (default: \texttt{False}) enables non-interactive mode, in which all user input and confirmation is disabled. Note that in non-interactive mode, the \texttt{confirm\_install} option is set to \texttt{False}, and if \texttt{auto\_rerun} is \texttt{False}, \texttt{davos} will throw an error if a smuggled package cannot be reloaded.
\item \texttt{.pip\_executable}: The path to the \texttt{pip} executable used to install smuggled packages. Default is programmatically determined from the Python environment and falls back to \texttt{sys.executable -m pip} if one can't be found.
\item \texttt{.suppress\_stdout}: If \texttt{True} (default: \texttt{False}), suppress all unnecessary output issued by both \texttt{davos} and the installer program. Useful when smuggling packages that need to install many dependencies and/or generate extensive output. If the installer program throws an error, both stdout and stderr will be shown with the traceback.
\end{itemize}

\noindent The top-level \texttt{davos} namespace additionally defines a handful of convenience functions for setting and checking \texttt{davos}'s active/inactive state (\texttt{davos.activate()}; \texttt{davos.deactivate()}; \texttt{davos.is\_active()}) as well as the \texttt{davos.configure()} function, which allows setting multiple config fields at once.

>>>>

\subsubsection{The \texttt{davos} config}\label{subsec:config}
The \texttt{davos} config provides a simple, high-level interface for controlling various aspects of \texttt{davos}'s behavior. After importing \texttt{davos}, the \texttt{davos.config} object (a singleton) exposes a number of configurable options as attributes that can be assigned different values, checked at runtime, and displayed in the notebook cell output (see Fig.~\textcolor{red}{INSERT REF TO ILLUSTRATIVE EXAMPLE FIG} for example usage). These include:
%The \texttt{davos.config} object provides a simple, high-level interface for controlling various aspects of \texttt{davos}'s behavior. After importing \texttt{davos}, the config instance (a singleton) for the current session exposes a number of options that can be set by assigning values to the object's attributes (see Fig.~\textcolor{red}{INSERT REF TO ILLUSTRATIVE EXAMPLE FIG} for example usage). These include:
%The \texttt{davos} config object provides a simple, high-level interface that allows users to view and set various options that affect \texttt{davos}'s behavior. After importing \texttt{davos}, the config instance (a singleton) for the current session is available as \texttt{davos.config}, and its various fields are accessible as attributes (see Fig.~\textcolor{red}{REF TO ILLUSTRATIVE EXAMPLE FIG} for example usage). The config object exposes a mixture of writable and read-only fields. Writable fields include:
\begin{itemize}
\item \texttt{.active}: This option allows users to disable \texttt{davos} functionality (i.e., support for \texttt{smuggle} statements and onion comments) for subsequent notebook cells by setting its value to \texttt{False}. \texttt{davos} can be re-enabled at any time by setting this option to \texttt{True} (the default when \texttt{davos} is first imported). See Section~\ref{subsec:implementation} for additional info.
\item \texttt{.auto\_rerun}: This option controls how \texttt{davos} behaves when attempting to \texttt{smuggle} a new version of a package that was previously imported and cannot be reloaded. This can happen if the package includes extension modules that dynamically link C or C++ objects to the Python interpreter itself, and the code that generates those objects was changed between the old and new versions. If this option is set to \texttt{True}, \texttt{davos} will automatically restart the notebook kernel and rerun all code up to (and including) the current \texttt{smuggle} statement. If \texttt{False} (the deafult), \texttt{davos} will instead issue a warning, pause execution, and prompt the user with buttons to either restart and rerun the notebook, or continue running with the previously imported package version until the next time the kernel is restarted manually. (Note: not configurable in Google Colaboratory).
%\item \texttt{.auto\_rerun}: Some packages (e.g., \texttt{numpy}, \texttt{pandas}) contain extension modules that dynamically link C or C++ objects to the Python interpreter when imported. If \texttt{davos} is used to \texttt{smuggle} a specific version of such a package after a different version of the same package was previously imported
%\item \texttt{.auto\_rerun}: This option controls how \texttt{davos} behaves when attempting to \texttt{smuggle} a new version of a package that was previously imported (at a different version) and cannot be reloaded (i.e., because it contains C-extensions that dynamically generate code). If \texttt{True} (default: \texttt{False}), \texttt{davos} will automatically restart the notebook kernel and rerun all code up to (and including) the current \texttt{smuggle} statement. Otherwise, \texttt{davos} will issue a warning, pause execution, and prompt the user with buttons to either restart and rerun the notebook or continue running with the imported package version. (Note: not configurable in Google Colaboratory).
\item \texttt{.confirm\_install}: If \texttt{True} (default: \texttt{False}), \texttt{davos} will require user confirmation (\texttt{[y]es/[n]o} input) before installing a smuggled package.
\item \texttt{.noninteractive}: Setting this option to \texttt{True} (default: \texttt{False}) enables non-interactive mode, in which all user input and confirmation is disabled. Note that in non-interactive mode, the \texttt{confirm\_install} option is set to \texttt{False}, and if \texttt{auto\_rerun} is \texttt{False}, \texttt{davos} will throw an error if a smuggled package cannot be reloaded, rather than prompting the user.
\item \texttt{.pip\_executable}: This option's value specifies the path to the \texttt{pip} executable used to install smuggled packages. The default is programmatically determined from the Python environment and falls back to \texttt{sys.executable -m pip} if no executable can be found.
\item \texttt{.suppress\_stdout}: If \texttt{True} (default: \texttt{False}), suppress all unnecessary output issued by both \texttt{davos} and the installer program. This can be useful when smuggling packages that need to install many dependencies and/or generate extensive output. If the installer program throws an error, both the stdout and stderr streams will be displayed with the traceback.
\end{itemize}

%\noindent The \texttt{davos.config} object also provides a few informative read-only fields, including: 
%\begin{itemize}
%\item \texttt{.environment}: This field's value is a short string describing the notebook environment in which \texttt{davos} is currently running. This is used internally may be one of \texttt{IPython<7.0} (a notebook whose frontend uses the Jupyter JavaScript library and whose backend uses an IPython version older than v7.0), \texttt{IPython>=7.0} (, or \texttt{}
%\end{itemize}
\noindent The top-level \texttt{davos} namespace also defines a handful of convenience functions for setting and checking \texttt{davos}'s active/inactive state (\texttt{davos.activate()}; \texttt{davos.deactivate()}; \texttt{davos.is\_active()}) as well as the \texttt{davos.configure()} function, which allows setting multiple config options at once.
